\textbf{International Transport costs:\\New Findings from modeling additive costs}\\Online Appendix (Not for Publication)

### 2021-10-11 redaction/JEGeo/revision_JEGeo/referees/answers/Answer_referee1.tex

 Alternatively, our method rather starts from the definition of transport costs as:
     $$\ln f_{ik} = \ln\left(\tau_{is(k)} -1 + \frac{t_{is(k)}}{\widetilde{p}_{ik}}\right) +\varepsilon_{ik}$$
\noindent from which we deduce the additive/multiplicative costs $\widehat{t}_{is(k)}$, $\widehat{\tau}_{is(k)}$ (on a mode/yearly basis). Then, relying on the Hummels' equation, one can deduce the share of additive costs in total transport costs $\beta_{ik}$ through Equation (\ref{eq:beta_TC}), again on a mode/yearly basis.

In this respect, the referee's method and our's are equivalent, in that they both allow to uncover the share of additive costs in total transport costs $\beta$, as well as the value of each trade costs component ($t,\tau$), that vary over time and sectors (and transport mode). Put it differently, our method is consistent with Hummel's methodology - provided that it is adequately reported as such. In comparison with \cite{hummels2007}, one supplementary advantage of our method is that we estimate a $\beta$ that varies over time, origin country and sector. Section 4 ([Section 3] of the submitted version) explores the importance of allowing for such a variability in accounting for the sources of the transport costs time trend. We agree that this was not sufficiently transparent in the submitted version. We hope that the revised version now fits the referee's expectations on this point.

\end{itemize}

\paragraph{b) The costs are high}
\begin{itemize}
\item[Concern 1] The suggested estimation strategy implies having much less data to exploit, for two reasons.
\begin{enumerate}
\item Information about the port of entry are only available since 1989, which is already smaller than our full sample starting
in 1974. On top of that, because of the Covid situation, the US Bureau of Census was only able to send them the CDs relative to the years 1997-1999 and 2001-2019. Implementing the referee's method would hence necessarily reduce the time coverage of our analysis by more than 20 years (skipping the 1974-1996 years in particular). In our view, the historical coverage is interesting per se, as it provides useful insights about how transport costs have evolved over time. Eliminating this dimension of the paper would be detrimental to its value-added.
\item As underlined before, the method is run country by country, and 3-digit sector by 3-digit sector, exploiting the variability within each country-3d sector across 10-d sub-sectors and ports of entry. Yet, it appears that for many couples (country, 3-digit sector), there is too few variability across sub-sectors or ports en entry given the number of fixed effects included in the regression, such that estimation can not be run. This can be seen comparing the number of observations by year/ transport mode with our method / with the referee's method reported in Table \ref{tab_comp_referee1_baseline}. Put it differently, this methodology discards countries which export a limited range of goods to the US and/or which arrive in the USA through the same ports of entry. In this respect, the induced selection bias may reduce the general scope of the transport costs estimates. This concern might yet be mitigated by noticing that the covered value of trade flows is only slightly lower. If it reduces the sample of sectors and origin countries covered, this method preserves the majority of trade flows in value.

@@

    \begin{table}[htbp]
	\caption{Comparison 2005-2013}
	\begin{center}		
		\input{Comp_baseline_referee1_reshaped.tex}

{\parbox[l]{12cm}{ \vspace{4pt}\footnotesize{Notes: Mean values reported for the 2005 and 2013 values for $\beta$. Time trend coefficient is the annual growth rate.}}}
\end{center}
	\label{tab_comp_referee1_baseline}%
\end{table}%
   \end{enumerate}

Following the referee's advice, we thus run this alternative estimation method as robustness check. Table \ref{tab_comp_referee1_baseline} reports the estimation results, by transport mode, in the Column ``Alternative'', along with the results obtained with our baseline method over the same period 2005-2013. As noted above, the partners-sectors covered are lower. Regarding the share of additive costs $\beta$, the comparison between the two methods goes in opposite directions depending on the transport mode. While the estimated $\beta$ is lower for maritime transport with the alternative method (also displaying a larger decrease over the period), the opposite holds for Air transport. In any case yet, the share of additive costs remains substantial, around 40\% on average over the period. In this respect, it confirms the main message of our paper shedding light on the importance of the additive component in international transport costs.

@@

In most cases, the log of the ratio is negative, implying a lower interval confidence of the $\beta$ estimate with our methodology. Our method undoubtedly yields more accurate estimations of the share of additive components, whatever the transport mode considered. We have checked that a similar conclusion applies on other years (they are not reported here for sake of brevity but they are available upon request).

One explanation of the limited accuracy with the alternative method might be the following. Given that the estimation method is run at the country-sector level (exploiting heterogeneity \textit{within} a given country-sector pair), it implicitly assumes that transport costs are independent \textit{across} sectors and across origin countries. Put it in plain words, it means that transport costs of say, cars, have nothing in common whether those goods comes from France or from Germany; or that transport costs that apply to imported goods from France have no common component across sectors. One might view this as a disputable assumption. From a statistical point of view further, it implies leaving aside information contained in the fact that transport costs have a both a country-specific component and a sector-specific component, that could explain the lower accuracy of the estimation.

\end{itemize}
\end{itemize}

All these elements, in particular Concern 2 regarding the lower accuracy of the estimates, drive us to maintain our original estimation as benchmark method in the revised version. However, we also want to keep track of this alternative method as further robustness check. For this purpose, we have amended the online Appendix with a section devoted to the referee's method (\textbf{Section D.3}). We deeply hope to convince you of the relevance of this choice.

@@

\subsection{Critique 2: Calculation of Unit Prices}

\textit{My second critique concerns the way the authors are calculating the unit prices.
The Census data reports the quantity of goods per observation. So, the authors
can calculate the unit price as Value/Quantity, which is consistent with how
price is modeled in standard trade models. Instead, the authors calculate unit
price as Value/Weight. This used to be a common exercise in the past where
many data-sets did not report Quantity. But, given their data, there is no
justification for the authors to calculate the prices this way.}

\textit{Calculating the unit price as Value/Weight presents the authors
with an additional endogeneity problem. To elaborate, let $\omega_{ik} = Weight/Quantity$
denote the unit weight of the goods in observation $ik$. [...] There is evidence that (i) $\omega_{ik}$ varies significantly within narrowly-defined product
categories, and (ii) $\omega_{ik}$ is negatively correlated with transport costs. So the
way the authors are calculating unit prices and estimating the model creates a
new (but avoidable) source of endogeneity.}

% MEMO: DO NOT FORGET TO REPORT THE ARGUMENTATION BELOW IN THE MAIN TEXT XXX
\paragraph{Our answer:}
\noindent The referee definitely has a point here, in the sense that Census data do report the quantity of goods. At a more fundamental level, this raises the following question: Do we have reason to believe our measure of unit prices generate significant deviations from the one relying on quantities? This referee's remark echoes recent findings by \cite{Lashkaripour_JIE2020}: based on US data very similar to ours over the period 1995-2015, the paper highlights, among other results, that the unit weight of imported goods is indeed substantially heterogeneous even within narrowly-defined product categories and the cost of transportation increases more rapidly with unit weight than the cost of production. Finally, \cite{Lashkaripour_JIE2020} finds that accounting for the heterogeneity in export unit weights provides evidence in favor of the iceberg cost assumption regarding transport costs. This result of transport costs close to be totally iceberg is quite different from our own findings of additive costs representing 30 to 45\% of total costs. The two stories are not necessarily incompatible, however. Beyond a longer time span, our database is exhaustive, and encompasses all goods and industries, while \citet{Lashkaripour_JIE2020}) restricts to indivisible/discrete goods representing a bit more 56\% of US total imports of goods. In this regard, when comparing Tables 1 and 10 in \citet{Lashkaripour_JIE2020}, one can see that the share of multiplicative costs tends to decrease with the share of discrete goods. It is therefore reasonable to think that the inclusion of all goods, like in our setting, would move the average share of multiplicative costs far from 100\%.

Nevertheless, the point made by the referee is an important one and deserves careful investigation. We devoted a lot of thought to a potential switch from weight to quantity. Running the estimation considering quantities (i.e., units) rather than weight, still on the transport mode-yearly basis yet appears really uneasy in our context for several, non-trivial reasons:

\begin{enumerate}
\item In the original Hummel's database which we use from 1974 to 2004, we don't have information on quantity by transport mode. This is incompatible with our empirical strategy of estimation transport costs which is conditional on the transport mode, similarly as in \cite{hummels2007}. We could restrict observations to single-mode flows, but that would alter our sample in a non-trivial way, raising some potential selection biases. Investigating this possibility shows that this would reduce the total value of trade flows from around 32,000 billion dollars, to 7,000 billion dollars, i.e. a reduction of flows by a factor of 4.5.

\item Even on this very reduced sample, units are not available for many years over our period, especially in the 1970s and the 1980s; this is particularly problematic considering that the time length is crucial for the assessment of transport costs long-run dynamics, which is one of the main objectives of the paper. \textbf{LP: Je ne suis pas sure de cet argument. Veut-on dire que dans les "quantity", en fait on trouve de tout mais pas des unites? }

\item Time length is especially important considering that, in the 1970s, trade composition was significantly different from today, with more goods for which correlation between weight and quality is likely to be less obvious \textbf{XXX GUILLAUME: EXAMPLES XXX}. At a more fundamental level, one may argue that considering the unit price as value/weight is relevant in our setting where we seek to identify transport costs. For instance, it makes sense that the shipment costs of cars do depend not only on the quantity of cars exported, but on the weight it makes, which is related to the volume it takes in the plane or the vessel. \textbf{XXX GUILLAUME: Do we have evidence, even anecdotal, on this point? LP: Sinon, laisser tomber cet argument}

    \item Considering the US census data which complete the original \cites{hummels2007} database, it is true that we can retrieve information on quantities. Specifically, this can be obtained crossing HS-10 product information with the correspondence table between the HS-6 product classification and the associated units (kg, tons, liters, numbers, etc.) also provided by the US Census. We are able to collect information since 2009. Investigating this database, it appears that in many 3-digit sectors, there are more than one type of quantities reported (for instance, sector \textbf{XXX} includes goods both recorded in terms of \textbf{YYY} and \textbf{ZZZ}.) To identify a proper unit price, we consequently reduce the flows to the 3-digit sectors reporting a single quantity.
    \item As discussed above, in our baseline regression we separate each transport cost component in its two distinct sector-origin country dimensions. As in \cite{Irrazabal_2015}, we assume an additive form for the additive cost, i.e. $t_{is(k)} = t_i+t_{s(k)}$ with $i$ the origin country and $s$ the sector. In the specific case of quantities, this raises a non-trivial issue yet. Specifically, imposing a country $i$ fixed effect would imply that the cost of sending one unit of say, tee-shirt from France is the same than sending one unit of say, car; and that this cost would be added to the sector-fixed effect. This does not seem to us as a reasonable assumption; in this case specifically, skipping the separability assumption does appear as the appropriate choice.

        As a consequence, we run the estimation on a reduced sample (\textbf{specify the number of years, value to trade flows in comparison with the full sample}), according to the following equation:

\begin{equation}
\ln\left(\frac{p_{ik}}{p^u_{ik}}-1 \right)= \ln \left(\tau_{is(k)} -1+\frac{t_{is(k)} }{p^u_{ik}} \right) + \epsilon_{ik} \label{eq:model_IetA}
\end{equation}
\noindent where $p^u_{ik}$ refers to the unit price associated with quantity. Depending on the sector, two different units are considered, kilograms and numbers.

The results are the following ... \textbf{To DEVELOP}

### 2021-10-11 redaction/JEGeo/revision_JEGeo/referees/answers/Answer_referee2.tex

\begin{equation}
p_{ikt}= \sum_i \sum_t \alpha_{it}^\tau \mathbbm{1}_{it}\widetilde{p}_{ikt} +  \sum_k \sum_t \alpha_{kt}^\tau \mathbbm{1}_{kt}\widetilde{p}_{ikt} + \sum_i \sum_t \alpha_{it}^t \mathbbm{1}_{it} + \sum_k \sum_t \alpha_{it}^t\mathbbm{1}_{kt} \label{eq:ref2}
\end{equation}

\textbf{Our answer:} As highlighted by the referee, our estimated equation imposes to use non-linear estimation methods, such as Non-Linear Least Squares. We agree that resorting on a linear form as the one suggested by the referee would substantially alleviate the computational burden. It does not seem to solve the issue yet.

First, it can be noticed that the equation suggested by the referee does not stand in accordance with the assumption we borrow from \cite{Irrazabal_2015}, that ad-valorem costs is decomposed in its two country/sector dimensions multiplicatively (i.e. approximating $\tau_{is(k)}$ by the product $\tau_i\times \tau_{s(k)}$.

However, even with another formulation, such as the equations (\ref{eq:ref2_basis}) and (\ref{eq:ref2}) suggested by the referee, we would still be constrained to resort to non-linear estimators. This is due to the restrictions imposed \textit{ex-ante} on parameters, i.e. $\tau \geq 1$ and $t\geq 0$, the latter meaning simply we constrain both types of transport costs to be non-negative, as by construction we cannot have $p_{ikt} < \widetilde{p}_{ikt}$. Without these restrictions, standard linear, least squares estimates deliver aberrant values with more than mild quality-of-fit. Taking into account this constraint implies that the error term should be always positive, which we ensure by specifying the error term such that:

\begin{equation*}
\frac{p_{ik}}{\widetilde{p}_{ik}}-1 =\left(\tau_{i}\times \tau_{k} -1+\frac{t_{i} + t_{k}}{\widetilde{p}_{ik}} \right)\times \exp(\epsilon_{ik})
\end{equation*}
\noindent where $\epsilon_{ik}$ follows a normal law centered on 0.

This specification obviously requires a non-linear estimation. We did our best to make the point clear in the revised version (see p.8). We also devote more time to the robustness of the empirical specification. On top of the robustness to the separability assumption (already in the submitted version), we also assess the robustness to the degree of aggregation and endogeneity (Section 3.4). We hope that this new version now convinces you that our estimation strategy is both relevant and robust.

### 2021-10-11 redaction/JEGeo/revision_JEGeo/referees/answers/general_answer_editor_revision.tex

Considering the lack of credible perspective to access this additional data in a sufficiently close/foreseeable future, we completed the revision with the following data: a full dataset at the SITC5 level, completed with systematic robustness checks (see the list at the end of this e-mail) based on a HS10 dataset over the 2002-2019 period. These new estimates do not provide any substantial change to our benchmark estimates, and it seems reasonable to consider that additional checks including years from the 1980s and the 1990s would not dramatically change this outcome. \medskip

To get now more precisely to the revisions undertaken, we thank the referees for their various comments which led to substantial improvements of the paper. We enclose detailed answers to the referees. Below we first detail how we handled two major points raised by both referees, before listing the other major changes brought to the paper.

\section{Two Common Concerns: Estimation Method and Big Picture}
Both referees questioned (i) our empirical methodology, especially our choice for a non-linear estimator and (ii) the lack of a ``big picture'' in the paper, i.e. of a deeper analysis of the implications of our results. Below we detail how we answered their concerns:\medskip

\subsection{Estimation Method}
Both referees debated our choice for a non-linear estimator, suggesting alternative functional forms estimable with standard linear estimators. We do acknowledge that the initial version of the paper did not make a clear enough case for the non-linear estimator. We now explain in details, both in the papers and in our answers to reviewers, the reasons why a non-linear estimator is unavoidable in our case. This is due to the restrictions imposed \textit{ex-ante} on parameters, i.e. $\tau \geq 1$ and $t\geq 0$, the latter meaning simply we constrain both types of transport costs to be non-negative, as by construction we cannot have $p_{ikt} < \widetilde{p}_{ikt}$. Without these restrictions, standard linear, least squares estimates deliver aberrant values with more than mild quality-of-fit. Taking into account this constraint necessarily brings a functional requiring a non-linear estimation. We did our best to make the point clear in the revised version (see p.8). \medskip

That said, resorting to non-linear estimations requires some assumptions due to the computational burden. The revised version devotes much more space to explicit tests of robustness of the empirical specification. On top of the robustness to the separability assumption (already in the initially submitted version), we also assess the robustness to the degree of data aggregation and endogeneity (Section 3.3) - see the list of modifications in section 2 from this letter. \medskip

In this regard, we also point in our answers that implementing the methodology suggested by Referee 1 would imply non-negligible costs. Firstly, this would leave us much less data to exploit, partly  because of the already mentioned CoViD issues - we would lose half of the years in the sample. Secondly, we show in details in our response that our method yields a more precise estimation of transport costs than the referee's method. \medskip

\subsection{Big Picture}
Both referees asked us to shed light on the implications of additive costs (the ``Big Picture''). The revised version answers this concern in two points. \medskip

Firstly, we maintain the analysis of the transport costs time trends (previously [Section 3], now Section 4); but we made our best to make this section easier to read, leaving the technical aspects in the Appendix (Section C). As such, we hope that the main message of this Section is better catched. \medskip

Secondly, and more importantly, we now emphasize the ``Big Picture'' implications of additive costs on theoretical grounds. Both referees suggested various, interesting paths to explore. Obviously, all of them could not be handled in a single paper. Therefore, we decide to focus on the welfare implications of our results.  Through the lens of the Melitz's (2003) model amended to integrate additive costs, we analyze the welfare gains that derive from the reduction in international transport costs that we have estimated (in Section 3 of the revised version), to quantify the extra welfare gains attributable to the reduction of the additive component. This analysis is driven in a new Section 5. We emphasize that the theoretical implications of additive costs have not been fully exhausted in Irarrazabal et al. (2015), Hornok and Koren (2015a,b), Alessandria et al. (2010), or Sorensen (2014). Specifically, we make use of our empirical results to investigate the welfare consequences of the reduction in international transport costs observed over 1974-2019, contrasting two cases: when this reduction is achieved through a combined reduction in the ad-valorem and the additive components (as quantied by our empirical model) or solely through the ad-valorem cost (as standardly modelled in New Trade theoretical approaches). To the best of our knowledge, this is the first time that such an assessment is preformed based on long-time, detailed trade data.
\medskip

Overall, these results appear to add a substantial contribution to the paper : we are able to provide a quantitative assessment of the welfare gains induced by the decrease in both types (additive and multiplicative) of costs over a 45-year period, and to highlight the respective part of each component in the determination of these gains. Note also that not only the inclusion of additive costs in the underlying framework generates large welfare differences, but also that the latter are probably a lower bound of the welfare variations induced by changes in additive \emph{trade} costs, larger than the sole transport costs.

\section{List of major revisions in the new version.}

Below we list the main other revisions implemented to answer referees' concerns:

@@

\begin{enumerate}

\item \emph{Endogeneity issues}: Section 3.3.2 and Appendix B.3 provides detailed developments answering concerns expressed by Referee 1 concerning potential endogeneity in our estimates. Relying on instrumental variables suggested by Referee 1, we provide first- and second-stage estimates, based on both at the 5-digit-product level and the more disaggregated HS10 level for sensitivity checks. Figure 3 on page XX reports our benchmark estimates by transport mode, together with their instrumented counterpart. In all cases, these estimates are very similar, when not identical. This supports that our benchmark estimates do not suffer any substantial biases arising from endogeneity concerns.

\item \emph{Aggregation issues}: Referee 1 pointed `` \emph{The original annual Census data reports trade at the origin country-HS10 product-district level of aggregation, whereas the authors are aggregating up the data even further to the origin country-HS5 industry-year level. Such an aggregation comes with strong implicit assumptions and sacrifices a lot of useful variation in the data}.'' Firstly, note these data are available only from 1989, whereas our full sample starts in 1974. Secondly, as already mentioned at the beginning of this letter, it was only possible to get access to the years 1997-1999 and 2001-2019, due to the COVID situation. Considering the importance of the time length for our empirical exercise, especially in the context of the exercise implemented in Section 5, we decided to stick to our initial 5-digit database, and to provide systematic robustness estimates based on the HS10 data available. These results are now reported in section 3.3.3 in the revised version. In particular, Table 3 and Figure 4 show the results are similar when using 10-digit product sand 5-digit products \textbf{XXX TO BE CONFIRMED XXX}

\item \emph{Calculation of unit prices}: Referee 1 is concerned by the fact that we calculate unit price as Value/Weight, instead of Value/Quantity. We explain in details in our answer why a potential switch from weight to quantity for calculating unit prices would be harmful in our context: until 2004, information on quantity \underline{by transport mode} is unavailable XXX + other arguments XXX Therefore, we decided to provide robustness estimates on a reduced sample (\textbf{specify the number of years, value to trade flows in comparison with the full sample}) \textbf{XXX TO BE COMPLETED XXX}

@@

\end{enumerate}

Altogether, we believe that the paper is much clearer and easier to read. The robustness exercises included in the main text focus on the elements that were the most problematic to the referees. We hope that you will be pleased by the outcome.

### 2021-10-13 redaction/JEGeo/revision_JEGeo/referees/answers/Answer_referee2.tex

We now answer in detail each of your comments given in italics.

\section{Detailed answers \label{sec:detailed_answers}}

\subsection{Implications/usefulness of the exercise}

\paragraph{``Big Picture''} \textit{[...] The fact that transport costs are both specific and ad-valorem is well known. Also, the theoretical implications of having specific, instead of ad-valorem (iceberg), transport cost when it comes to analyzing the consequences of further reductions in transport costs are by now quite well understood; see e.g. papers by Irarrazabal et al. (2015), Hornok and Koren (2015a,b), Alessandria et al. (2010), or Sorensen (2014). The main contribution of this paper thus appears to be to unravel the temporal evolution / relative importance of the ad-valorem and specific transport cost component. However, besides showing this evolution, the paper is basically silent on the implication(s) of the patterns found. In the conclusion, the authors state that this is left for future research. This was quite disappointing, simply documenting the evolution of these two components leaves the reader (at least me) wondering why he/she should care about this. The authors should aim to be much more clear on what the trends in ad-valorem / specific transport costs mean/imply from the perspective of these recent theoretical contributions/insights.} 
\smallskip
\paragraph{Exploring the heterogeneity of our results} \textit{At the very least the authors could/should make use of the fact that the temporal patterns in specific / ad-valorem transport costs is likely to show substantial heterogeneity across goods as well as countries. Exploring this heterogeneity to a fuller extent could already hint at the main drivers (insurance costs / containerization / economies of scale) behind the observed patterns. This could be done by e.g. not only reporting the mean and median of the ad-valorem / specific transport cost components but exploring more fully the heterogeneity in these transport costs components across sectors/exporters. Also, it should be relatively straightforward to provide some analysis of the major correlates with the identified specific and ad-valorem costs (e.g. product value/weight ratio, distance to the exporter, etc.).}
\smallskip

\textbf{Our answer:} We devoted a lot of thought to this point, which directly echoed a similar concern by the other referee. The latter writes: ``\emph{Does this observation revise our understanding of say the gains from trade? Does it shed new light on a puzzle many people are thinking about?
One crude suggestion is to see how the reduction in the industry-specific cost terms is related to the industry-level trade elasticities. If the composition effects favor low-elasticity industries, the findings in the paper may have first-order implications for the gains from trade. Another suggestion is to dig deeper into the relative rate at which additive and multiplicative transport costs have declined over time. Since additive transport costs favor rich (high-quality exporting) countries, the disproportionally greater reduction in additive costs can perhaps explain the rise of low-income exporter as documented by Hanson (2012, JEP).}''

All in all, your suggestions and those of the other referees pointed in two directions for the ``Big Picture'' implications of our exercise: either exploring the compositional country-product dynamics underlying of our results, or focusing on the implications regarding grains from trade. Both paths were undeniably worth exploring, but could not be followed in a single paper. Therefore, we decided to focus on the second path, i.e. to  offer insights on the welfare implications of our results. In this regard, the new Section 5 ``The role of additive cost: Theoretical insights'' is devoted to a theory-based analysis of the alterations to welfare gains involved by the relative variations of additive and multiplicative transport costs over our period of analysis.

Our choice to dig into the welfare implications of our results has two main motivations. Firstly, even if ``\emph{the fact that transport costs are both specific and ad-valorem is well known}'', some recent literature still debates the practical importance of additive costs - for example, \cite{Lashkaripour_JIE2020} recently finds (though in a different theoretical setting) support for the iceberg trade cost assumption, i.e, iceberg accounting for almost all trade costs. Secondly, the theoretical implications of additive costs have not been fully exhausted in \citet{Irrazabal_2015}, Hornok and Koren (2015a,b), Alessandria et al. (2010), or \citet{sorensen2014}. More specifically, we start from the canonical \cites{melitz} model where we add additive trade costs. The inclusion of additive costs in a \citet{melitz} setting has already been performed in \citet{sorensen2014} and \citet{Irrazabal_2015}. However, \citet{sorensen2014} exclusively performs a theoretical analysis, without any quantitative exercise. In addition to a partial equilibrium extension of \citet{melitz}, \citet{Irrazabal_2015} do perform a quantitative simulation to assess the welfare variations induced by the presence of additive costs, but the latter is based on a calibration for transport costs restricted to 2004, based on the case of Nowrway. In contrast, our own exercise relies on a several decades time span for the US, allowing us to highlight the welfare alterations induced over time by the relative dynamics of additive and multiplicative costs, based on ``true'' values for the latter - remember that our methodology allows for the identification of both multiplicative and additive costs as a share of total costs, whereas additive costs in \citet{Irrazabal_2015} are expressed relatively to the (median) export price. \textbf{XXX COMPLETE WITH OUR CONTRIBUTIONS WRT TO Hornok and Koren (2015a,b), Alessandria et al. (2010)XXX}

@@

Table 5 in Section 5 of the paper reports the results of these various comparative statics exercises for Air and Vessel transport modes. Specifically, we report the change in total transport costs decomposed in its two dimensions (additive and ad-valorem); as well as the welfare change, both in absolute and in relative terms. Qualitatively, the conclusions are identical for both transport modes, with two major insights. First, for a given decrease in total transport costs,  welfare gains are around 50\% higher when this reduction is partly achieved through a reduction in the additive costs. Second, the decrease in export sunk costs (i.e., increase in the share of exporting firms) proportionally amplifies the gains from decreasing variable costs, with again an additional premium coming from the decrease of additive costs.

Overall, these results appear to add a substantial contribution to the paper : we are able to provide a quantitative assessment of the welfare gains induced by the decrease in both types (additive and multiplicative) of costs over a 45-year period, and to highlight the respective part of each component in the determination of these gains. Note also that not only the inclusion of additive costs in the underlying framework generates large welfare differences, but also that the latter are probably a lower bound of the welfare variations induced by changes in additive \emph{trade} costs, larger than the sole transport costs.

%\textbf{WHAT DO WE DO ABOUT THAT? We provide an analysis by sector about the time trends. Do more than that: Regress the additive costs/ ad-valorem costs $t_{is}$, $\tau_{is}$ on distance from the US? correlation btw each component and the sector/country fixed effect ?}
